---
title: "Introduction to dsci-310-group-6-pkg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dsci-310-group-6-pkg-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(datatheexplorer)
```

When working with data to find the patterns or make predictions, we usually need to explore the data and use training set and testing set to tune our model.

This document introduces you to dsci-310-group-6-pkg’s basic set of tools, and shows you how to apply them to data frames.

### Data: sample_data & mydata
To explore the basic data manipulation verbs of dsci-310-group-6-pkg, we’ll use the dataset sample_data. This data frame has three columns and three rows.

```{r}
dim(sample_data)
sample_data
my_data <- data.frame(x = c(1, 2, 3, 4, 5),
                      y = c(10, 20, 30, 40, 50),
                      z = c(100, 200, 300, 400, 500))
```
### Read&Clean&Export data with `cleandata()`
cleandata() allows you to read the data from the given path, discard the given columns and export the data into the given destination path. Both the first two arguments are quoted paths, which are of string type. The last argument is a list containing the quoted column names.

For example, we can read the data, discard the "x" column and choose not to export the new dataframe.
```{r}
input_path <- here::here('data/sample_data.csv')
clean_data(input_path = input_path, NULL, "x")
```

### Find the maximum value of a column in the data with `getmax()`
getmax() allows you to find the maximum value of a column in a given dataset. The first argument is a data frame. The second argument is a quoted column name which you want to find the maximum value for.

For example, we find the 
```{r}

```
